|

### 2022-07-24 manuscript.Rmd
whitespace

According to LinkedIn's 2017 U.S. Emerging Jobs Report, machine learning engineers and data scientists rank among the top emerging jobs.
With the urgent need for training a higher number of skilled data scientists, many institutes of higher education are developing their own data science curricula, and a consensus on what should be included in such curricula has not yet been reached. 
In the latest version of *Computing Competencies for Undergraduate Data Science Curricula* by ACM Data Science Task Force, accessibility is a recommended content for the data science curricula [@danyluk2021computing].

>>>>

According to LinkedIn's 2017 U.S. Emerging Jobs Report, machine learning engineers and data scientists rank among the top emerging jobs (cite).
With the urgent need for training a higher number of skilled data scientists, many institutes of higher education are developing their own data science curricula. However, a consensus on what should be included in such curricula has not yet been reached. 
In the latest version of *Computing Competencies for Undergraduate Data Science Curricula* by ACM Data Science Task Force, accessibility is a recommended content for the data science curricula [@danyluk2021computing].
